Funding programmes for early career researchers do/not influence their independence

### 2023-06-09 _targets.Rmd
changes in tar_download

  tarchetypes::tar_download(ids_path,
      urls = Sys.getenv("link_to_supervisors"),
      paths = here::here("data", "raw", "supervisors.csv")),
  tarchetypes::tar_download(gender_path,
      urls = Sys.getenv("link_to_gender"),
      paths = here::here("data", "raw", "names4api_tagged.tsv")),
  tarchetypes::tar_download(authors_arrow_path,
      urls = Sys.getenv("link_to_updated_authors"),
      paths = here::here("data", "raw", "authors_by_pubs.arrow")),
  tarchetypes::tar_download(text_arrow_path,
      urls = Sys.getenv("link_to_updated_texts"),
      paths = here::here("data", "raw", "riv_text.arrow")),
   tarchetypes::tar_download(sup_path,
      urls = Sys.getenv("link_to_supervisors_control"),
      paths = here::here("data", "raw", "supervisors_control_final.csv")),

>>>>

  tarchetypes::tar_download(ids_path,
      urls = Sys.getenv("link_to_supervisors"),
      paths = here::here("data", "raw", "supervisors.csv")),
  tarchetypes::tar_download(gender_path,
      urls = Sys.getenv("link_to_gender"),
      paths = here::here("data", "raw", "names4api_tagged.tsv")),
  tarchetypes::tar_download(authors_arrow_path,
      urls = Sys.getenv("link_to_updated_authors"),
      paths = here::here("data", "raw", "authors_by_pubs.arrow"),
       mode = "wb"),
  tarchetypes::tar_download(text_arrow_path,
      urls = Sys.getenv("link_to_updated_texts"),
      paths = here::here("data", "raw", "riv_text.arrow"),
      mode = "wb"),
   tarchetypes::tar_download(sup_path,
      urls = Sys.getenv("link_to_supervisors_control"),
      paths = here::here("data", "raw", "supervisors_control_final.csv")),

### 2023-06-09 article.Rmd
changes in tar_download

# Print table for treatment level 1
kable(table_before_1, digits = 3, caption = "Descriptive statistics for treatment group") %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

@@

# Print table for treatment level 0
kable(table_before_0, digits = 3, caption = "Descriptive statistics for unfunded control group") %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

@@

# Print table for treatment level 2
kable(table_before_2, digits = 3, caption = "Descriptive statistics for funded control group") %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

>>>>

# Print table for treatment level 1
kable(table_before_1, digits = 3, caption = "Descriptive statistics for treatment group") 
  # %>% kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

@@

# Print table for treatment level 0
kable(table_before_0, digits = 3, caption = "Descriptive statistics for unfunded control group") %>%
  # kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

@@

# Print table for treatment level 2
kable(table_before_2, digits = 3, caption = "Descriptive statistics for funded control group") %>%
  # kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
